%--------------------------------------------------%
% Resume in Latex                                  %
% Author: Sami Warraich <samiwarraich51@gmail.com> %
% License: MIT                                     %
%--------------------------------------------------%

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item[]\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} &  {\small#2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-6pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{\small#1} & {\small #2} \\
    \end{tabular*}\vspace{-6pt}
}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-4pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------

\begin{center}
    \textbf{\Huge \scshape Sami Ullah Warraich} \\ \vspace{1pt}
    \small 
    {\underline{Riyadh, Saudi Arabia}} $|$ 
    \href{https://wa.me/+966583490073}{\underline{+966583490073}} $|$ 
    \href{mailto:samiwarraich51@gmail.com}{\underline{samiwarraich51@gmail.com}} $|$ 
    \href{https://linkedin.com/in/samiwarra1ch}{\underline{LinkedIn}} $|$
    \href{https://github.com/samiwarraich}{\underline{GitHub}} 
    $|$ \href{https://sami.warraich.co}{\underline{Portfolio}}
\end{center}


%-----------Professional Summary-----------

\section{Professional Summary}
    \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     {Full Stack Developer with 3+ years of experience in building web and mobile applications. Specialized in React, React Native, and Node.js. Proven track record of delivering efficient and scalable solutions across diverse projects. Committed to continuous learning and innovation in software development.} 
    }}
 \end{itemize}




%-----------PROFESSIONAL EXPERIENCE-----------
\section{Professional Experience}
  \resumeSubHeadingListStart
  \resumeSubheading
      {Software Engineer @ Dabeeb}{May 2022 - Present}{}{}\vspace{-12pt}
      \resumeSubSubheading{Dabeeb ARS}{}
      \resumeItemListStart
        \resumeItem{Currently working on the frontend of an Expo mobile application for peer-to-peer accommodation rentals. Developing UI components and implementing features such as property listing, booking management, user reviews, and payment integration screens.}
    \resumeItemListEnd
      \resumeSubSubheading{Dabeeb FMS}{}
      \resumeItemListStart
        \resumeItem{Contributed to the frontend development of a web-based fleet management system using React.js. Implemented interactive dashboards for real-time vehicle tracking, maintenance scheduling, and performance analytics.}
    \resumeItemListEnd
      \resumeSubSubheading{Dabeeb ERP}{}
      \resumeItemListStart
        \resumeItem{Created a full-stack inventory management application with React Native frontend, Express.js and Hasura backend, integrating VendHQ API. Focused on enhancing system capabilities and streamlining operations across multiple branches.}
    \resumeItemListEnd
    \resumeSubSubheading{Dabeeb App}{}
      \resumeItemListStart
        \resumeItem{Developed a comprehensive mobile application using React Native, Express.js, and Hasura for scooter and bicycle rentals. Implemented robust user authentication, real-time availability tracking, and integrated secure payment processing.}
    \resumeItemListEnd
    \resumeSubheading
      {Jr. Software Engineer @ Gigalabs}{Feb 2021 - Mar 2022}{}{}\vspace{-12pt}
      \resumeSubSubheading{Linesheets}{}
      \resumeItemListStart
        \resumeItem{Contributed to the development of an online platform for customizing and sharing product collections. Implemented key features using React.js for the frontend and Express.js for the backend, enhancing user experience and platform functionality.}
    \resumeItemListEnd
    \resumeSubSubheading{New York Adventure Club}{}
      \resumeItemListStart
        \resumeItem{Worked on a tour company platform providing insider access to city secrets. Developed both frontend and backend components using React.js and Express.js, focusing on improving tour booking and management systems.}
    \resumeItemListEnd
    \resumeSubSubheading{Bukit}{}
      \resumeItemListStart
        \resumeItem{Developed components for a marketplace connecting end-users to operators via white-labeled SaaS technology. Utilized Next.js for the frontend, Express.js for the backend, and MongoDB for data management, contributing to a seamless aggregator experience.}
    \resumeItemListEnd
    \resumeSubSubheading{Furniture Bank California}{}
      \resumeItemListStart
        \resumeItem{Developed a platform connecting people with excess furniture to those in need. Implemented frontend and backend solutions using Next.js and MongoDB, streamlining the furniture donation and distribution process.}
    \resumeItemListEnd
      \resumeSubSubheading{Financial Tracking System}{}
      \resumeItemListStart
        \resumeItem{Contributed to the frontend development of a transaction and inventory management system using React.js. Focused on creating intuitive interfaces for financial data visualization and management. (Client did not disclose the name of the project)}
    \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Skills}
  \resumeSubHeadingListStart
    \resumeSubheading
    {Languages \& Frameworks}{}{}{}\vspace{-12pt}
      \resumeItemListStart
        \resumeItem{JavaScript, TypeScript, React.js, Next.js, React Native, Expo, Node.js, Express.js, GraphQL, HTML, CSS, Redux, Tailwind, Bootstrap, and SQL.}
    \resumeItemListEnd
    \resumeSubheading
      {Tools \& Platforms}{}{}{}\vspace{-12pt}
      \resumeItemListStart
        \resumeItem{VS Code, Git, Gitlab, Github, Postman, Docker, MongoDB, PostgreSQL, Firebase, Vercel, Heroku, Hasura, Linux, Microsoft Office, Mattermost, Slack, Trello, Jira, and Asana.}
    \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------PERSONAL PROJECTS-----------
\section{Personal Projects}
  \resumeSubHeadingListStart
    \resumeSubheading
    {Taskify}{}{}{}\vspace{-12pt}
      \resumeItemListStart
        \resumeItem{Developed a collaborative task management platform using Next.js and PostgreSQL. Implemented features for organization and board creation, card management with drag-and-drop functionality, and integrated payment processing.}
    \resumeItemListEnd
    \resumeSubheading
    {Pixel Muse}{}{}{}\vspace{-12pt}
      \resumeItemListStart
        \resumeItem{Developed a suite of automated bots using Next.js and Node.js for generating and distributing random color pixel images across Twitter and Telegram platforms. Implemented image generation algorithms and social media API integrations.}
    \resumeItemListEnd
    \resumeSubheading
    {Phanox}{}{}{}\vspace{-12pt}
      \resumeItemListStart
        \resumeItem{Developed a full-stack e-commerce platform specializing in headphone sales using Next.js, Sanity, and Stripe. Implemented features including product cataloging, user authentication, shopping cart functionality, and secure payment processing.}
    \resumeItemListEnd
      \resumeSubheading
      {Bookit}{}{}{}\vspace{-12pt}
      \resumeItemListStart
        \resumeItem{Created an online reservation system using Next.js, Stripe, and MongoDB to streamline the booking process for hospitality businesses. Implemented real-time availability updates, user account management, and integrated payment gateway for seamless transactions.}
    \resumeItemListEnd
    \resumeSubheading
    {Shopit}{}{}{}\vspace{-12pt}
      \resumeItemListStart
        \resumeItem{Built an e-commerce application using React.js, Express.js, Stripe, and MongoDB. Developed features such as product search, filtering, user reviews, and order management to enhance the online shopping experience.}
    \resumeItemListEnd
  \resumeSubHeadingListEnd

    %-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Gujrat Institute of Management Sciences (PMAS AAUR)}{Gujrat, Pakistan}
      {Bachelor of Science (Computer Science)}{}
  \resumeSubHeadingListEnd

%-----------ACADEMIC PROJECTS-----------
\section{Academic Project}
  \resumeSubHeadingListStart
      \resumeSubheading
      {Find Friend (Final Year Project)}{}{}{}\vspace{-12pt}
      \resumeItemListStart
        \resumeItem{Developed a mobile application using React Native and Firebase for real-time chat and location sharing. Implemented features including user-to-user messaging, real-time location tracking with Google Maps integration, and route visualization.}
    \resumeItemListEnd
  \resumeSubHeadingListEnd


\end{document}